\appendix
\section{Implementation Evidence Appendix}
This appendix maps claims to generated implementation reports. Supported claims may be used as main-text implementation claims; partial claims should be described as implementation support rather than validation evidence.

\begin{table*}[t]
\centering
\small
\caption{Claim-level evidence summary generated from implementation reports.}
\label{tab:claim-evidence-summary}
\begin{tabular}{p{0.06\linewidth}p{0.10\linewidth}p{0.36\linewidth}p{0.22\linewidth}p{0.18\linewidth}}
\hline
ID & Status & Claim & Primary report & Key metrics \\
\hline
C01 & supported & Unified experience memory stores simulation and pseudo-real episodes with gap/calibration fields. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/summary\_report.json} & entry\_count=12; source\_distribution=\{"pseudo\_real": 8, "simulation": 4\}; gap\_count=4; calibration\_count=4 \\
C02 & supported & Real-format import and pseudo-real evidence exercise sim-real pair, gap, and sandbox calibration paths. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/real\_format\_evidence\_pack.json} & real\_format\_entry\_count=8; pseudo\_real\_entry\_count=8; sim\_entry\_count=4; paired\_gap\_count=4; sim\_real\_gap\_count=4; sensor\_gap\_entry\_count=0; +3 more \\
C03 & partial & Shared real-format memory stores RGB-D, lidar, and wrist-force evidence and can derive conservative sensor-gap summaries. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/real\_format\_evidence\_pack.json} & sensor\_evidence\_entry\_count=0; rgbd\_evidence\_entry\_count=0; lidar\_evidence\_entry\_count=0; wrist\_force\_evidence\_entry\_count=0; sensor\_modality\_distribution=\{\}; sensor\_gap\_entry\_count=0 \\
C04 & supported & Candidate plans can be shadow-rolled out in sandbox and scored before selection. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/sandbox\_rollout\_g4\_place\_occupied.json} & candidate\_count=4; selected\_before\_sandbox=g4\_avoid\_occupied\_primary; selected\_after\_sandbox=g4\_avoid\_occupied\_primary; candidate\_changed\_by\_sandbox=False; critic\_status\_counts=\{"pass": 4\} \\
C05 & supported & Stage-aware retrieval renders planner context separating generation, ranking, rewrite, and writeback evidence. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/stage\_planner\_context\_g4.json} & context\_count=1; stage\_context\_token\_count\_avg=252; stage\_context\_distinct\_memory\_count\_avg=6; stage\_specificity\_score\_avg=0.7056; risk\_evidence\_count\_total=2; critic\_warning\_count\_total=4 \\
C06 & supported & Visual keyframes are used as an auxiliary retrieval signal during candidate ranking. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/visual\_retrieval\_ablation\_g3\_clean.json; results/memory/universal\_pipeline\_calibration\_v1/visual\_retrieval\_ablation\_g4\_place\_occupied.json} & visual\_index.indexed\_entry\_count=12; visual\_index.indexed\_image\_count=60; g3.selected\_candidate\_before\_visual=g3\_default; g3.selected\_candidate\_after\_visual=g3\_place\_first; g3.selected\_candidate\_change=True; g3.retrieval\_changed\_rate=0.3333; +2 more \\
C07 & supported & Gap-derived calibration changes sandbox initial state and contributes an explicit risk penalty. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/sandbox\_calibration\_ablation\_g4\_place\_occupied.json} & candidate\_id=g4\_avoid\_occupied\_primary; object\_start\_delta\_score\_only\_vs\_no\_calibration=0; object\_start\_delta\_full\_vs\_no\_calibration=0.12; sandbox\_score\_delta\_score\_only\_vs\_no\_calibration=0; sandbox\_score\_delta\_full\_vs\_no\_calibration=0; raw\_sandbox\_score\_delta\_score\_only\_vs\_no\_calibration=-0.12; +13 more \\
C08 & supported & LLM-generated lessons are audited for grounding, validity, concision, and conflicts before policy use. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/lesson\_quality\_report\_g4\_place\_occupied.json} & lesson\_count=1; avg\_lesson\_length=7; max\_lesson\_length=7; avg\_field\_length=4.5; max\_field\_length=7; evidence\_id\_valid\_rate=1; +8 more \\
C09 & supported & Sandbox critic identifies risky candidates and increases safety evidence under stress variants. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/safety\_stress\_g4\_place\_occupied.json} & memory\_sandbox\_critic.risky\_candidate\_selected\_rate=0; memory\_sandbox\_critic.safe\_candidate\_selected\_rate=1; memory\_sandbox\_critic.risky\_warn\_or\_block\_rate=1; memory\_sandbox\_critic.critic\_warn\_rate\_avg=0.2; full\_stage\_lesson\_sandbox.risky\_candidate\_selected\_rate=0; full\_stage\_lesson\_sandbox.safe\_candidate\_selected\_rate=1; +2 more \\
C10 & supported & Under adversarial ranking stress, sandbox critic redirects selection away from artificially boosted risky candidates. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/harder\_safety\_stress\_g4\_place\_occupied.json} & memory\_only\_risky\_selected\_count=4; sandbox\_prevented\_risky\_selection\_count=4; sandbox\_prevented\_risky\_selection\_rate=1; selection\_changed\_by\_sandbox\_count=4; sandbox\_risky\_selected\_count=0 \\
C11 & supported & Closed-loop writeback stores executed experiences and retrieves them in later ranking passes. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/writeback\_benchmark\_g3\_clean.json} & round\_count=3; write\_count=3; entry\_count\_delta=2; new\_memory\_retrieval\_rate=1; selected\_candidate\_change\_rate=0.3333; score\_delta\_after\_writeback\_avg=0.0273; +1 more \\
C12 & supported & The experience library represents multiple robot memory types rather than only flat episode logs. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/memory\_type\_coverage\_report.json} & entry\_count=12; covered\_memory\_type\_count\_avg=5.667; entries\_covering\_all\_memory\_types=8; entries\_covering\_all\_memory\_types\_rate=0.6667; temporal\_memory.coverage\_rate=1; spatial\_memory.coverage\_rate=1; +4 more \\
C13 & supported & Text-semantic summaries provide an auxiliary retrieval signal over structured experience fields. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/text\_semantic\_memory\_report.json} & entry\_count=12; semantic\_summary\_nonempty\_count=12; semantic\_summary\_nonempty\_rate=1; avg\_token\_count=148.8; semantic\_signal\_rate=1; query\_count=9; +3 more \\
C14 & supported & Real LLM-generated recovery-plan candidates can be semantically validated, sandboxed in parallel, critic-ranked, and exported as a validated robot plan. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/llm\_plan\_candidate\_search\_g3\_clean\_real\_llm\_report.json} & dry\_run\_llm=False; llm\_provider=doubao; num\_plans\_requested=2; num\_plans\_normalized=2; sandboxed\_plan\_count=2; failed\_worker\_count=0; +8 more \\
C15 & supported & Multi-candidate LLM plan search evaluates more recovery alternatives than a single-plan LLM baseline before selecting a validated plan. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/llm\_plan\_search\_ablation\_g3\_clean\_real\_llm.json} & plan\_count\_delta=1; sandboxed\_plan\_count\_delta=1; accepted\_plan\_count\_delta=1; best\_sandbox\_score\_delta=0; unique\_step\_sequence\_delta=1; single\_final\_status=accept; +19 more \\
C16 & supported & Field-atomic execution experiences are converted into parameter priors for later LLM planning. & \texttt{/tmp/field\_atomic\_memory\_report.json} & field\_atomic\_entry\_count=3; field\_atomic\_success\_count=3; field\_atomic\_failure\_count=0; prior\_action\_count=0 \\
C17 & supported & Cold-start and writeback rounds show whether field-atomic memory is exposed to the planner as explicit context. & \texttt{/tmp/field\_atomic\_ablation.json} & dry\_run\_llm=True; cold\_memory\_count=0; warm\_memory\_count=3; warm\_prior\_action\_count=3; parameter\_changed\_count=0; action\_set\_changed=False; +2 more \\
C18 & supported & Field-atomic execution traces expose action-level tracking error, gripper commands, and direct-qpos usage for debugging. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/field\_atomic\_trace\_summary.json} & trace\_count=10; action\_count=5; success\_count=10; failure\_count=0; direct\_qpos\_true\_count=0; direct\_qpos\_false\_count=10; +2 more \\
C19 & supported & Rewrite-loop ablation reports separate supported component evidence from missing true sequential LLM rewrite evidence. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/rewrite\_loop\_ablation\_report.json} & variant\_count=5; status\_counts=\{"supported": 5\}; sequential\_rewrite\_report\_count=1; has\_single\_plan\_baseline=True; has\_multi\_candidate\_critic\_ranking=True; has\_sequential\_critic\_feedback\_rewrite=True; +17 more \\
C20 & supported & Physical sandbox rollouts can sweep control and scene perturbations to expose sensitivity to pose, delay, gain, and gripper effects. & \texttt{/tmp/physical\_sandbox\_perturbation\_report.json} & rollout\_count=6; success\_count=0; task\_success\_count=6; failure\_label\_counts=\{"object\_not\_lifted": 6, "skill\_failed:verify\_grasp": 6, "verify\_grasp": 6\}; nominal.success\_rate=0; nominal.success\_rate\_delta\_vs\_nominal=0; +10 more \\
C21 & supported & Core skill defaults are audited to prefer physical actuator execution over direct-qpos shortcuts. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/physical\_default\_audit\_report.json} & file\_count=26; direct\_qpos\_true\_total=0; direct\_qpos\_false\_total=20 \\
C22 & supported & Memory writeback is auditable through explicit write, skip, merge, and reject decisions. & \texttt{/tmp/write\_policy\_audit\_report.json} & entry\_count=3; decision\_counts=\{"write": 3\}; reason\_counts=\{"preserve\_field\_atomic\_experience": 3\}; preserved\_reason\_counts=\{"preserve\_field\_atomic\_experience": 3\}; memory\_role\_counts=\{"field\_atomic\_success": 3\} \\
C23 & supported & Write-policy pressure tests exercise all lifecycle decisions: write, merge, skip, and reject. & \texttt{results/memory/universal\_pipeline\_calibration\_v1/write\_policy\_pressure\_report.json} & case\_count=6; stored\_library\_entry\_count=3; decision\_counts=\{"merge": 1, "reject": 1, "skip": 1, "write": 3\}; reason\_counts=\{"accepted": 1, "duplicate\_low\_risk\_success": 1, "low\_value\_success": 1, "missing\_required\_fields": 1, "preserve\_failure\_taxonomy": 1, "preserve\_field\_atomic\_experience": 1\}; expected\_decisions\_present=\{"merge": true, "reject": true, "skip": true, "write": true\} \\
C24 & supported & Runtime scene observations have a fixed schema for converting onsite RGB-D/LiDAR outputs into sandbox scene construction inputs. & \texttt{/home/mlx/mujoco/YOLO\_World-SAM-GraspNet/experience\_system/templates/field\_runtime\_scene\_observation\_template.json} & schema\_exists=True \\
\hline
\end{tabular}
\end{table*}

\paragraph{Summary.}
Claim count=24; supported=23; missing reports=0; status distribution=\{"partial": 1, "supported": 23\}.

\paragraph{Safe wording boundaries.}
\noindent\textbf{C01.} Safe: The memory library stores simulation and pseudo-real experiences using a unified schema with gap and calibration fields. Avoid: Do not claim true real-robot validation from this report.\\
\noindent\textbf{C02.} Safe: The implementation supports real-format episode import and uses pseudo-real evidence to exercise sim-real pairing, gap extraction, and sandbox calibration, and shows calibration consumed by sandbox rollout reports. Avoid: Do not claim real-robot validation or real-robot success-rate improvement unless true real-source execution reports are added.\\
\noindent\textbf{C03.} Safe: The implementation supports real-format sensor evidence fields for RGB-D, lidar, and wrist-force observations, and can derive conservative sensor-gap summaries from those stored observations. Avoid: Do not claim real-robot success-rate improvement or validated sensor-derived calibration effects from this row alone.\\
\noindent\textbf{C04.} Safe: Candidate plans are shadow-executed in MuJoCo and fused with memory scores before selection. Avoid: Do not claim a full digital twin or real-world execution success.\\
\noindent\textbf{C05.} Safe: Planner context is assembled from stage-specific memory evidence separating positive examples, risk priors, critic evidence, and writeback histories. Avoid: Do not claim a learned multi-stage planner.\\
\noindent\textbf{C06.} Safe: Visual keyframes are indexed and used as an auxiliary retrieval signal during candidate ranking. Avoid: Do not claim broad multimodal semantic reasoning.\\
\noindent\textbf{C07.} Safe: Gap-derived calibration changes sandbox initialization and contributes an explicit risk penalty during candidate evaluation. Avoid: Do not claim dynamics, friction, or full contact-model calibration; this ablation covers object initial-state shift and score penalty.\\
\noindent\textbf{C08.} Safe: Generated lessons are checked for evidence grounding, candidate/skill validity, concision, and internal conflicts before being used for policy adjustment. Avoid: This is a static quality audit for generated lessons, not proof of learned policy rules.\\
\noindent\textbf{C09.} Safe: The sandbox critic identifies unsafe candidates and increases the safety margin in stress reports. Avoid: Do not claim selection changed if memory-only already selected a safe candidate.\\
\noindent\textbf{C10.} Safe: Under adversarial ranking stress with artificially boosted risky candidates, sandbox critic can redirect selection away from the risky candidate. Avoid: This stress test uses artificial ranking perturbations; do not claim the same selection change occurs in the unperturbed policy.\\
\noindent\textbf{C11.} Safe: Newly executed experiences can be written back and retrieved by later candidate ranking passes. Avoid: Do not claim statistically proven long-horizon success-rate improvement.\\
\noindent\textbf{C12.} Safe: The experience library stores multi-type robot memories, with temporal, spatial, episodic, semantic, perceptual, and sim-real gap evidence represented by explicit fields. Avoid: Do not claim broad RoboMME-scale coverage or real-robot sensor validation from this report; the report measures field-level coverage in the current library.\\
\noindent\textbf{C13.} Safe: The system constructs explicit text-semantic summaries from scenario, condition, task, anomaly, failure taxonomy, critic, gap, and retrieval-key fields, and uses TF-IDF vectors indexed by FAISS as an auxiliary semantic retrieval signal. Avoid: Do not claim this is a learned language encoder or neural embedding benchmark; the report measures lightweight TF-IDF + FAISS semantic retrieval only.\\
\noindent\textbf{C14.} Safe: A configured external LLM generated multiple recovery-plan candidates; the system normalized them, validated skill preconditions/effects, ran parallel MuJoCo sandbox rollouts, ranked by critic/sandbox status, and exported a validated\_robot\_plan for dry-run dispatch. Avoid: Do not claim real-robot execution success, arbitrary unseen-skill planning, or statistically proven superiority over all single-plan baselines.\\
\noindent\textbf{C15.} Safe: The multi-candidate search evaluates more LLM-generated recovery alternatives than a single-plan baseline, runs valid candidates through parallel sandbox rollout, and selects a critic-approved validated plan. Avoid: Do not claim a success-rate improvement from this small G3 clean ablation alone; both variants succeeded in the current smoke.\\
\noindent\textbf{C16.} Safe: The system stores successful and failed field atomic experiences and uses them as explicit parameter priors for later planning. Avoid: Do not claim this proves improved real-robot success without a real-robot ablation.\\
\noindent\textbf{C17.} Safe: Field atomic writeback can be reloaded as explicit planner\_input priors in a subsequent planning round. Avoid: Do not claim parameter improvement from dry-run LLM if the mock plan is deterministic; use real LLM or varied goals for parameter-change evidence.\\
\noindent\textbf{C18.} Safe: Field-atomic executions expose action-level trace summaries, including final tracking error, gripper command, control mode, and direct-qpos usage for onsite debugging. Avoid: Do not claim these summaries prove real-robot tracking accuracy; they summarize MuJoCo or stored experience traces only.\\
\noindent\textbf{C19.} Safe: Existing reports support single-plan validation, multi-candidate critic ranking, memory-backed risk evidence, field-atomic parameter-prior exposure, and a dry-run sequential critic-feedback rewrite attempt. Avoid: Do not claim critic-feedback rewriting improves recovery unless the underlying report has rewrite\_rounds > 0 and final\_sandbox\_status=accept under a real LLM or clearly stated dry-run setting.\\
\noindent\textbf{C20.} Safe: The physical MuJoCo sandbox can sweep pose, delay, gain, and gripper perturbations and report which failures are sensitive to those controls. Avoid: Do not claim real-driver calibration or real-robot robustness without measured hardware response data.\\
\noindent\textbf{C21.} Safe: Core base, torso, arm, gripper, and field atomic defaults have been audited to prefer physical control over direct-qpos shortcuts. Avoid: Do not claim that every explicit debug or test path is physical-only; the audit concerns defaults, not every possible parameter override.\\
\noindent\textbf{C22.} Safe: The write policy is auditable: each candidate entry receives an explicit write, skip, merge, or reject decision with a reason. Avoid: Do not claim the write policy is learned or globally optimal; it is an explicit engineering gate.\\
\noindent\textbf{C23.} Safe: A deterministic pressure test constructs representative experiences that trigger write, merge, skip, and reject decisions, showing that writeback is not a plain append-only log. Avoid: Do not claim the handcrafted pressure cases prove optimal memory lifecycle policy.\\
\noindent\textbf{C24.} Safe: The implementation defines a field runtime observation template for converting onsite perception outputs into sandbox scene inputs. Avoid: Do not claim automatic high-fidelity scene reconstruction until real perception outputs are mapped and validated onsite.\\
